---
title: "Enhancing Chemotherapy Response Prediction via Matched Colorectal Tumor-Organoid Gene Expression Analysis and Network-Based Biomarker Selection"
subtitle: "WGCNA --- Main model"
author: "Wei Zhang, Hanchen Huang, Xi S.Chen"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_document:
    highlight: pygments
    theme: yeti
    toc: true
    number_sections: true
    df_print: paged
    code_download: false
    toc_float:
      collapsed: yes
    toc_depth: 3
editor_options:
  chunk_output_type: inline    
---

```{r setup, include=FALSE}
# Initial settings
knitr::opts_chunk$set(echo = TRUE, message = F)

dir.base <- "../../"
# Create and retrieve dir
dir.data <- file.path(dir.base, "data/")

# Create results dir
dir.results <- file.path(dir.base, "analysis-results/")
dir.results.wgcna <- file.path(dir.results, "WGCNA/")
for(p in grep("dir",ls(),value = T)) dir.create(get(p),recursive = TRUE,showWarnings = FALSE)
```

# Auxillary function

```{r message = F}
fn_ls <- list.files("../utility/", pattern = ".R", full.names = T)
for (f in fn_ls) source(f)
```

# Load data

```{r}
train_df <- prepare_train_df()
exp_top_genes <- train_df$exps_ls
```

```{r}
# Creat exp set
expSet <- list(
  GSE171680 = list(data = scale(t(exp_top_genes$GSE171680))),
  GSE171681 = list(data = scale(t(exp_top_genes$GSE171681))),
  GSE64392 = list(data = scale(t(exp_top_genes$GSE64392)))
)
checkSets(expSet)
```

# WGCNA

```{r}
powers = 2:20

# Call the network topology analysis function
sft1 = pickSoftThreshold(
  expSet$GSE171680$data,            
  blockSize = 30,
  powerVector = powers,
  networkType = "signed",
  verbose = 5
  )

sft2 = pickSoftThreshold(
  expSet$GSE171681$data,             
  blockSize = 30,
  powerVector = powers,
  networkType = "signed",
  verbose = 5
  )

sft3 = pickSoftThreshold(
  expSet$GSE64392$data,             
  blockSize = 30,
  powerVector = powers,
  networkType = "signed",
  verbose = 5
  )
```

```{r eval = F}
modules <- blockwiseConsensusModules(
  multiExpr = expSet,
  power = 12, 
  networkType = "signed",
  TOMType = "signed",
  TOMDenom = "mean",
  networkCalibration = "full quantile",
  detectCutHeight = 0.999,
  minModuleSize = 30,
  saveConsensusTOMs = T,
  saveIndividualTOMs = T
)
```

# Identification of key module

## Find eigen modules that most related to outcome

```{r}
# Prepare survival data
GSE171682c <- train_df$survival
```

```{r}
# RFS
rfs_results <- cox_coef(modules$multiMEs$GSE171680$data %>% t(),
                        GSE171682c,
                        time_var = "rfs_month",
                        event_var = "recur")
```

```{r}
rfs_results %>% arrange(pr_z)
```

```{r}
## OS
cox_results_os <- cox_coef(modules$multiMEs$GSE171680$data %>% t(),
                        GSE171682c,
                        time_var = "os_month",
                        event_var = "death")
```

```{r}
cox_results_os %>% arrange(pr_z)
```

```{r}
## Corr
ls <- plyr::ldply(
  1:ncol(modules$multiMEs$GSE171680$data),
  .fun = function(i){
    cr <- cor.test(modules$multiMEs$GSE171680$data[,i],
                   modules$multiMEs$GSE171681$data[,i], method = "spearman")
    data.frame(cor = cr$estimate, p = cr$p.value, method = "Spearman")
  }
)
rownames(ls) <- gsub("ME", "", colnames(modules$multiMEs$GSE171680$data))
```

## Calculate consensus kME

```{r}
kME <- consensusKME(
  multiExpr = expSet,
  moduleLabels = modules$colors,
  multiEigengenes = modules$multiMEs
)
```


```{r eval = F}
# Save WGCNA modules and hub genes
save(
  modules,
  exp_top_genes,
  kME,
  cox_results,
  cox_results_os,
  corr_results,
  file = file.path(dir.results.wgcna,"WGCNA_GSE171682_GSE64392_results.rda")
)
```

# Select hub genes in key modules

```{r}
load(file.path(dir.results.wgcna,"WGCNA_GSE171682_GSE64392_results.rda"))
```

```{r}
module_wo_grey <- modules$colors[!modules$colors %in% "grey"]
table(module_wo_grey)
```

```{r}
module_wo_grey_ls <- plyr::llply(
  unique(module_wo_grey),
  .fun = function(m){
    data.frame(gene = names(module_wo_grey[module_wo_grey == m]))
  }
)
names(module_wo_grey_ls) <- unique(module_wo_grey)
```

```{r}
writexl::write_xlsx(
  module_wo_grey_ls,
  file.path(dir.results.wgcna, "modules_from_wgcna.xlsx")
)
```

criteria

1) MM > 0.4
2) consistent in drug and os response 
3) ME p value < 0.05 in drug correlation 
4) significant in gene-drug correlation

```{r }
hub_gene_in_modules_drug <- get_top_genes_in_module(
 module_wo_grey, kME,
 thres_kME = 0.5
)
hub_gene_in_modules_drug <- hub_gene_in_modules_drug[hub_gene_in_modules_drug %>% 
                       purrr::map(~nrow(.) > 1) %>% 
                       unlist()]
```

```{r eval = F}
save(
  hub_gene_in_modules_drug,
  file = file.path(dir.results.wgcna, "WGCNA_key_modules_corr_pairs.rda")
)
```

# Session Information

```{r}
devtools::session_info()
```

