---
title: "Enhancing Chemotherapy Response Prediction via Matched Colorectal Tumor-Organoid Gene Expression Analysis and Network-Based Biomarker Selection"
subtitle: "WGCNA --- Model 1"
author: "Wei Zhang, Hanchen Huang, Xi S.Chen"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_document:
    highlight: pygments
    theme: yeti
    toc: true
    number_sections: true
    df_print: paged
    code_download: false
    toc_float:
      collapsed: yes
    toc_depth: 3
editor_options:
  chunk_output_type: inline    
---

```{r setup, include=FALSE}
# Initial settings
knitr::opts_chunk$set(echo = TRUE, message = F)

dir.base <- "../../"
# Create and retrieve dir
dir.data <- file.path(dir.base, "data/")

# Create results dir
dir.results <- file.path(dir.base, "analysis-results/")
dir.results.wgcna <- file.path(dir.results, "WGCNA/")
dir.results.test <- file.path(dir.results, "test/")
for(p in grep("dir",ls(),value = T)) dir.create(get(p),recursive = TRUE,showWarnings = FALSE)
```

# Auxillary function

```{r message = F}
fn_ls <- list.files("../utility/", pattern = ".R", full.names = T)
for (f in fn_ls) source(f)
```

# Load data

```{r}
exp_list <- prepare_single_train_df("GSE171682")
```

```{r}
# Creat exp set
expSet <- list(
  GSE171680 = list(data = scale(t(exp_list$exp$GSE171680)))
)
checkSets(expSet)
```

# WGCNA

```{r eval = F}
powers <- c(seq(1,20,by=1))
power_df <- pickSoftThreshold(expSet$GSE171680$data,
                      powerVector = powers,
                      verbose = 2,
                      networkType = "signed")
```

```{r eval = F}
modules <- blockwiseModules(
  datExpr = expSet$GSE171680$data,
  power = power_df$powerEstimate, 
  networkType = "signed",
  TOMType = "signed",
  detectCutHeight = 0.999,
  minModuleSize = 30,
  saveConsensusTOMs = F
)
```

# Identification of key module

## Find eigen modules that most related to outcome

```{r}
# Prepare survival data
GSE171682c <- exp_list$clinical
```

```{r}
cox_results <- cox_coef(modules$MEs %>% t(),
                        GSE171682c,
                        time_var = "rfs_month",
                        event_var = "recur")
```

```{r}
cox_results %>% arrange(pr_z)
```

tan, brown, darkgreen, red, royalblue, lightgreen, orange, darkgreen

```{r}
cox_results_os <- cox_coef(modules$MEs %>% t(),
                        GSE171682c,
                        time_var = "os_month",
                        event_var = "death")
```

```{r}
cox_results_os %>% arrange(pr_z)
```

orange, tan, darkgrey

## Calculate consensus kME

```{r}
kME <- signedKME(
  datExpr = expSet$GSE171680$data,
  datME = modules$MEs
)
```

```{r eval = F}
# Save WGCNA modules and hub genes
save(
  modules,
  kME,
  cox_results,
  cox_results_os,
  file = file.path(dir.results.wgcna,"WGCNA_GSE171680_results.rda")
)
```

# Select hub genes in key modules

```{r}
load(file.path(dir.results.wgcna,"WGCNA_GSE171680_results.rda"))
```

```{r}
module_wo_grey <- modules$colors[!modules$colors %in% "grey"]
table(module_wo_grey)
```

criteria

1) MM > 0.5
3) ME p value < 0.05 in os or rfs outcome

```{r }
hub_gene_in_modules_drug <- get_top_genes_in_module(
 module_wo_grey, kME,
 consensus = F
)
hub_gene_in_modules_drug <- hub_gene_in_modules_drug[hub_gene_in_modules_drug %>% 
                       purrr::map(~nrow(.) > 1) %>% 
                       unlist()]
```

```{r eval = F}
save(
  hub_gene_in_modules_drug,
  file = file.path(dir.results.wgcna, "WGCNA_key_modules_GSE171680_pairs.rda")
)
```

```{r}
load(file.path(dir.results.wgcna, "WGCNA_key_modules_GSE171680_pairs.rda"))
```

# Train organoid models

```{r}
test_GEO <- c(
  "GSE39582",
  "GSE17538",
  "COAD", #TCGA
  "GSE106584",
  "GSE72970",
  "GSE87211"
)
```

```{r}
# Get selected genes
selected_modules <- hub_gene_in_modules_drug[names(hub_gene_in_modules_drug) %in% c("tan", "orange", "darkgrey")]
selected_genes <- Reduce(rbind,selected_modules)$ID

# RF model
rf2 <- fit_rf(gene_select = selected_genes,
             exp = exp_list$exp$GSE171680,
             y = data.frame(os_month = exp_list$clinical$os_month, 
                            death = exp_list$clinical$death),
             mode = "VIMP",
             seed = 954,
             type = "survival")

# Ridge regression
set.seed(950)
ridge <- fit_ridge(
  gene_select = selected_genes,
  exp = exp_list$exp$GSE171680,
  y = Surv(time = exp_list$clinical$os_month, event = exp_list$clinical$death),
  type = "survival",
  family = "cox",
  type.measure = "C"
)

# Ensemble
set.seed(952)
ridge2 <- fit_ridge(
  gene_select = colnames(rf2$xvar),
  exp = exp_list$exp$GSE171680,
  y = Surv(time = exp_list$clinical$os_month, event = exp_list$clinical$death),
  a = 0,
  type = "survival",
  family = "cox",
  type.measure = "C"
)
```

## Test model

```{r}
results <- plyr::ldply(
  test_GEO,
  .fun = function(geo){
    
    cat("Testing GEO: ", geo, "\n")
    # Prepare testing df
    test_ls <- prepare_test_df(geo)
    
    # Test model
    ## Ridge
    cat("Ridge Test\n")
    ridge1_results <- prepare_results(
      model = "ridge",
      mod = ridge,
      test_list = test_ls
    )
    
    ## Ensemble
    cat("Ridge Test\n")
    ridge2_results <- prepare_results(
      model = "ridge",
      mod = ridge2,
      test_list = test_ls
    )

    cat("RF2 Test\n")
    rf2_results <- prepare_results(
      model = "RF",
      mod = rf2,
      test_list = test_ls
    )

    results_df <- rbind(
      ridge1_results, ridge2_results, rf2_results
    ) %>% 
      mutate(Model = c("ridge","ensemble","RF"),
             GEO = geo,
             gene_select_criteria = "Most variable GSE171680 WGCNA tan + orange + darkgrey",
             .before = 1)
    
    return(results_df)
  }
)

results$num_gene_total <- length(selected_genes)
```

# Session Information

```{r}
devtools::session_info()
```

